Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
added large small world

>>>>

Given that our model is only based on a sample of the population, we can say that it directly represents the "small world". It's using that sample we can create models, see relationships between variables, and make observations/findings. However, arguably more important, is the representation of the "large world". Using post-stratification, we are able to apply these findings on a much larger scale. The model very well represents many aspects of the real world population. However, it isn't a perfect match, as it only approximates real life. For example, these findings are well and good and in theory should perform well in the "large world", but we can't say for sure that it's a perfect match until we see it in action.
